\documentclass[]{rh-resume}
\fullname{Rafayet Hossain}
%\jobtitle{CS}

\begin{document}
\resumeheader
{\linkedin{rafayeth}}
{\email{rafayet@hos.sh}}
{\github{rafayet-git}}
{\phone{+1 917-385-8827}}
% {\website{hos.sh}}
{\nationality{United States}}

\begin{section}{Education}
    \begin{subsectionnobullet}{City University of New York - Hunter College}{B.A. Computer Science, Minor in Mathematics}{New York, NY}{Expected: May. 2027}
        \italicitem{GPA: 3.540}
        \italicitem{Relevant Courses: Software Analysis and Design 2, Calculus 2, Discrete Mathematics, Computer Architecture}
        \italicitem{Honors: Dean's list, Peter F. Vallone Academic Scholarship}
    \end{subsectionnobullet}
\end{section}

\begin{section}{Professional Experience}
    \begin{subsection}{Google Software Engineering Program (G-SWEP) via Basta}{Participant}{Remote}{Oct. 2024 - Dec. 2024}
        \item Selected as one of 200 participants for a 10-week program by Google and Project Basta.
        \item Collaborated with a Google Software Engineer for 10 weeks to receive mentorship to prepare for technical and behavioral interviews.
    \end{subsection}
\end{section}

\begin{section}{Projects}

\begin{subsectionproject}{PVD Image Steganography}{Personal}{\gitRepo{github.com/rafayet-git/pvd-image-steganography}{Project Repo}}
    \item{Developed an image steganography program in C++ that encodes/decodes text within an image, by manipulating the differences between RGB values per pixel, while keeping image quality intact.}
    \item{Used the FreeImage library for image processing and support for various image formats.}
    \item{Implemented custom classes and data structures, including queues, to improve programming encapsulation and efficiency. }    
\end{subsectionproject}

\begin{subsectionproject}{PySweeper}{Personal}{\gitRepo{github.com/rafayet-git/pysweeper}{Project Repo}}
    \item{Developed a Minesweeper game in Python using the Pygame library, by creating an user interface and handling input events.}
    \item{Utilized Pyinstaller and Github Actions to automate building executables for Windows, Linux, and macOS operating systems.}
\end{subsectionproject}

\end{section}

\begin{section}{Supporting Experience}
    \begin{subsection}{Creative Art Works}{Youth Apprentice}{New York, NY}{Jul. 2023 - Aug. 2023}
        \item Worked with 20+ other YAs and TAs to establish a mural inside the Bronx Family Court.
        \item Responsible for communicating with the client for design needs, and pitching ideas to be used for the final design.
    \end{subsection}
\end{section}

\sectiontable{Skills}{
    \entry{Programming Languages}{C/C++, Python, Java, HTML, CSS, Markdown, \LaTeX}
    \entry{Libraries \& Frameworks}{Matplotlib, Pygame, Pyinstaller, FreeImage, Processing}
    \entry{Applications \& Programs}{Git, GitHub, Linux, Make, Microsoft Office, Wireshark, Splunk, QEMU/KVM}
    % microsoft office, burp suite
}
\sectiontable{Certifications}{
    \entry{Codepath}{Intermediate Cybersecurity (CYB102) \hfill \textit{Feb. 2024 - Apr. 2024} \newline Advanced Technical Interview Prep (TIP103) \hfill \textit{Jun. 2024 - Aug. 2024} }
}



\end{document}
